Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-10 prop_letter.tex
a bit on section 2

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the set
of events is the set of \emph{projection operators} $P$. This set
includes the empty projection~$\mathbb{0}$, the identity
projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a
quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_i$ is associated with a probability $\mu(P_i)$ subject
to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$, we
have:
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}

@@

In conventional quantum theory (CQT), when we measure a property
$\mathbf{O}$ of a physical system whose state is represented by a
density matrix~$\rho$, the probability to obtain the value $\lambda$
of that property is determined by the Born rule
$\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
  P_{i}\right)$, where $P_{i}$ denotes the projector onto the
eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
Hermitian operator
$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Alternatively, one may say that the state $\rho$ determines the
probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
from the set $\events$ of all possible projectors $P$ onto the
interval $[0,1]$, and satisfies the following probability axioms~
\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
\item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
\item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_iP_j=\delta_{ij}P_i$,
we have 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
satisfying the above axioms, Gleason's theorem asserts that there
exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

>>>>

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events~\cite{Kolmogorov1950}.  In the quantum case, the
events of interests are the \emph{projection operators} $P$. This set
includes the empty projection~$\mathbb{0}$, the identity
projection~$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a
well-defined quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_i$ is associated with a probability $\mu(P_i)$ subject
to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set of
mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$, we
have:
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}

As an example, consider a three-dimensional Hilbert space with
orthonormal basis $\{\ket{0},\ket{1},\ket{2}\}$ and an observable $Q$
with spectral decomposition $\proj{1} + 2\,\proj{2} +
3\,\proj{3}$. Here are two fragments of valid probability measures
$\mu_1$ and $\mu_2$ that can associated with this space:
$\mu_1(\proj{0}) = 0.5$, $\mu_1(\proj{1}) = 0.5$,
$\mu_1(\proj{2}) = 0$, and $\mu_2(\proj{0}) = 0$,
$\mu_2(\proj{1}) = 0.5$, $\mu_2(\proj{2}) = 0.5$. By the Born rule,
the first probability measure corresponds to the quantum system being
in the state $1/\sqrt{2}(\ket{0}+\ket{1})$ and the second corresponds
to the quantum system being in the state
$1/\sqrt{2}(\ket{1}+\ket{2})$. The expectation value of the observable
is the first case is 1.5 and in the second it is 2.

@@

In conventional quantum theory (CQT), when we measure a property
$\mathbf{O}$ of a physical system whose state is represented by a
density matrix~$\rho$, the probability to obtain the value $\lambda$
of that property is determined by the Born rule
$\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)=\Tr\left(\rho
  P_{i}\right)$, where $P_{i}$ denotes the projector onto the
eigenspace corresponding to the eigenvalue $\lambda_{i}$ of the
Hermitian operator
$\mathbf{O}$~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Alternatively, one may say that the state $\rho$ determines the
probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as a function
from the set $\events$ of all possible projectors $P$ onto the
interval $[0,1]$, and satisfies the following probability axioms~
\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}:

\begin{itemize}
\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{0})=0$. 
\item $\mu_{\rho}^{\mathrm{B}}(\mathbb{1})=1$. 
\item $\mu_{\rho}^{\mathrm{B}}\left(\mathbb{1}-P\right)=
1-\mu_{\rho}^{\mathrm{B}}\left(P\right)$. 
\item For a set of mutually orthogonal projectors $\left\{ P_{i}\right\} _{i=1}^{N}$,
$P_iP_j=\delta_{ij}P_i$,
we have 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(\sum_{i=1}^{N}P_{i}\right)=
\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)
\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
satisfying the above axioms, Gleason's theorem asserts that there
exists a unique state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{B}}$
in a Hilbert space of dimension $d\geq3$~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
